Piecewise Regression for Nutritional Outcomes Pre- and Post-CFTR Modulator

### 2022-05-19 StatNet/knot_models.qmd
Update knot_models.qmd
random slope

@@

@@

-   How to handle truncated data (e.g. a value of "\< 0.1")?

@@

>>>>

## Pre-/Post-CFTR Modulator Results With Random Slope

```{r}
mod = lmer(Vitamin.D ~ Time + c1 + c2 + (Time|Patient.ID),data = cf)
plot_df = mod@frame
plot_df$pred = predict(mod)
ggplot(plot_df,aes(x = Time,y = Vitamin.D,group = factor(Patient.ID))) +
    geom_line(aes(y = pred),alpha = 0.5) + geom_point(aes(y = pred),alpha = 0.5) +
    theme_bw() + theme(legend.position = "none") + xlab("Time (years)")
```

## Pre-/Post-CFTR Modulator Results With Random Slope

@@

## Future Plans

-   Try a random slope
-   Apply similar models to other outcomes like sweat electrolytes, etc.

@@

-   Other ways handle truncated data (e.g. a value of "\< 0.1")?

    -   Tobit extension to the existing model?

@@

    -   How informative can we make these priors?
